Backpropagating Gravitational wave events

### 2022-03-14 src/ms.tex
Add paragraph on companion paper

The most important point in this paper is illustrated in figure \ref{fig:GW150914_M1_M2_q3}.
We can see the posterior samples in $M_1-M_2$ space are spatially correlated with $q_3$,
this means if we fixed the value of $q_3$ instead of allowing it to jointly vary with all other parameters,
we would miss the samples that do not match the fixed value of $q_3$.
Comparing our result with 
\kw{Add figure showing hyper-parameters are important to recovering the progenitor parameters incorrectly.}

@@

We present a new pathway to understand binary evolution with GW events in this paper.
Instead of forward modelling an assumed distribution of initial binary to the observed population,
we solve a root-finding problem to find the best initial binary parameters that reproduce the posterior distribution for each event. 
The most obvious advantage our method provides is it returns the joint posterior distribution of progenitor parameters and hyper-parameters for each event.
This enables a data-driven way to study the distribution of hyper-parameters,
i.e. once we have a catalog of events, each has their own set of posterior in the hyper-parameter space,
we can employ common techniques such as hierarchical Bayesian analysis to fit a population model to the distribution of hyper-parameters,
without making specific assumption such as fixing the hyper-parameters for all types of event.

\kw{Talk about GW150914.}

@@

% Single formation channel and fundamental limitation on that.
While our method allows data-driven exploration of the hyper-parameters space for the first time, there are a number of improvements can be implemented in future studies.
In this study we use only \texttt{COSMIC} as our evolutionary function, which by design cannot explain all the events in GWTC3.
For example, event with either of the component mass larger than the PISN gap such as GW190521 cannot be explained by \texttt{COSMIC}.
Alternative channels such as dynamic formation channel will be needed to explain some subset of the events in GWTC3.
As pointed out in the literature \kw{Cite mike}, it is unlikely that all the observed events in GWTC3 can be explained by a single formation channel.
As GW detectors sensitivity increase, we expect to see more and more events that are unusual in some way.
Therefore, having a self-consistence population synthesis code that contains multiple formation channels is essential to accommodate the growing catalog of GW events.

>>>>

The most important point in this paper is illustrated in figure \ref{fig:GW150914_M1_M2_q3}.
We can see the posterior samples in $M_1-M_2$ space are spatially correlated with $q_3$,
this means if we fixed the value of $q_3$ instead of allowing it to jointly vary with all other parameters,
we would miss the samples that do not match the chosen value of $q_3$.
By folding in the hyper-parameters into the root-finding algorithm,
we can capture the correlation between 
\kw{Dartboard comparsion} Comparing our result with 
\kw{Add figure showing hyper-parameters are important to recovering the progenitor parameters correctly.}

@@

We present a new pathway to understand binary evolution with GW events in this paper.
Instead of forward modelling an assumed distribution of initial binary to the observed population,
we solve a root-finding problem to find the best initial binary parameters that reproduce the posterior distribution for each event. 
The most obvious advantage our method provides is it returns the joint posterior distribution of progenitor parameters and hyper-parameters for each event.
This enables a data-driven way to study the distribution of hyper-parameters,
i.e. once we have a catalog of events, each has their own set of posterior in the hyper-parameter space,
we can employ common techniques such as hierarchical Bayesian analysis to fit a population model to the distribution of hyper-parameters,
without making specific assumptions such as fixing the hyper-parameters for all types of event.

In this work we showcase the power of the proposed method with two events, GW150914 and GW191129.
We show the joint posterior of the two events' progenitor parameters and hyper-parameters.
In particular, to the authors knowledge, this is the first time the correlation between progenitor parameters and hyper-parameters is shown.
Our work is not only a more efficient way to study GW events' progenitors,
but also allows the possibility of measuring the astrophysics related the binary evolution.

@@

% Single formation channel and fundamental limitation on that.
While our method allows data-driven exploration of the hyper-parameters space for the first time, there are a number of improvements can be implemented in future studies.
In this study we use only \texttt{COSMIC} as our evolutionary function, which by design cannot explain all the events in GWTC3.
For example, event with either of the component mass larger than the PISN gap such as GW190521 cannot be explained by \texttt{COSMIC}.
Alternative channels such as dynamic formation channel will be needed to explain some subset of the events in GWTC3.
As pointed out in the literature \kw{Cite mike}, it is unlikely that all the observed events in GWTC3 can be explained by a single formation channel.
As GW detectors sensitivity increase, we expect to see more and more events that are unusual in some way.
Therefore, having a self-consistence population synthesis code that contains multiple formation channels is essential to accommodate the growing catalog of GW events.
In this paper, our main focus is to illustrate the concept of "back-propagating" GW events posterior sample in this work,
highlighting the capability of our method and motivating the community to build the next generation population synthesis code that can work with our method.
To avoid cluttering of focus, we discuss the physical implication of the result presented in this work under our specific assumption (i.e. using \texttt{COSMIC} as our evolutionary function) in a companion paper.
